---
title: "Getting NBL Basketball stats using nblR"
author: "Jason Zivkovic"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting NBL Basketball stats using nblR}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  message=FALSE,
  warning=FALSE
)
```


## Overview

This vignette will outline how to use the functions in the `nblR` package to allow users to obtain clean and tidy data from the Australian National Basketball League (NBL).


## Installation


You can install the CRAN version of [**```nblR```** ](https://CRAN.R-project.org/package=nblR) with the below.

```{r cran-installation, eval=FALSE}
install.packages("nblR")
```


Alternatively, you can install the dev (little less stable) version of [**```nblR```**](https://github.com/JaseZiv/nblR/) from [GitHub](https://github.com/JaseZiv/nblR) with:

```{r gh-installation, eval=FALSE}
# install.packages("remotes")
remotes::install_github("JaseZiv/nblR")
```


```{r libraries}
library(nblR)
library(dplyr)
```


## Usage


The following code will show you how to get various different statistics for the Australian National Basketball League (NBL).


### Match Results

To get results of matches players in the NBL since the 1979 season, use the `nbl_results()` function. This function takes in one argument - `wide_or_long` (options either 'wide' or 'long').

Using `wide_or_long = "wide"`, the resulting data frame will have one row per match played, with the home and away team listed.

```{r match_results_wide}
results_wide <- nbl_results(wide_or_long = "wide")
dplyr::glimpse(results_wide)
```


Using `wide_or_long = "long"`, the resulting data frame will instead have two rows per match played, with both teams listed on a separate line.

```{r match_results_long}
results_long <- nbl_results(wide_or_long = "long")
dplyr::glimpse(results_long)
```


### Team Box Scores

To get box scores at the *team* level, use the `nbl_box_team()` function. This will return team box score data since the 2015-2016 season. Note, not all fields will contain data for earlier seasons.

```{r team_box}
team_box <- nbl_box_team()
glimpse(team_box)
```


### Player Box Scores

To get box scores at the *player* level, use the `nbl_box_player()` function. This will return player box score data since the 2015-2016 season. Note, not all fields will contain data for earlier seasons.

```{r player_box}
player_box <- nbl_box_player()
glimpse(player_box)
```


### Play-by-Play data

To get play-by-play data, use the `nbl_pbp()` function. This will return play-by-play data since the 2015-2016 season. Note, not all fields will contain data for earlier seasons.

```{r pbp}
pbp <- nbl_pbp()
glimpse(pbp)
```



### Shots data

To get shot location and type data, use the `nbl_shots()` function. This will return shooting data since the 2015-2016 season. Note, not all fields will contain data for earlier seasons.

```{r shots}
shots <- nbl_shots()
glimpse(shots)
```
